---
title: "Statistical computing"
author: "Dr. Ramsamy Geordan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = ""
)
```

Consider the Monthly Work Accident Data from Mauritius which spans over years 1991 to 2010
and named “data” in csv format. The data is provided to you in class or can be obtained on
moodle.

(a) You are requested to draw a normal boxplot to represent the work accident data by month
using R.

(b) You are requested to draw a revised boxplot using the Tufte's principle in the theory of
data graphics using R.

Your work must contain the graphs and also the R codes used to run the graphs. You will
present your findings to me in class as soon as you complete it.
Hint: To be able to do part (b), you will need to investigate the following packages:

(i) ggplot2

(ii) ggthemes

```{r}
library(ggplot2)
library(ggthemes)
library(tidyverse)
setwd("/home/geordan/Code/drive/R scripts/Revision Stat cop")
```

```{r}
df <- read.csv("./datasets/data - data.csv")
glimpse(df)
```

# Boxplot

```{r}
boxplot(Accident ~ Month, data = df)
```

# Revised boxplot

```{r}
# revised boxplot
# customize x ticks
# customize x axis label

sorted_data <- arrange(df, Month)
sorted_data %>%
  ggplot(aes(x = factor(Month), y = Accident, colour = factor(Month))) +
  geom_boxplot() +
  xlab("Month") +
  theme_tufte() +
  scale_x_discrete(breaks = c(1, 3, 5, 7, 9, 11), labels = c(
    "Jan", "Mar", "May", "Jul", "Sep",
    "Nov"
  )) +
  labs(colour = "Months") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Line graph 

```{r}
sales <- read.csv("./datasets/sales - sales.csv")
attach(sales)
plot(
  sales[, 2],
  ylim = c(0, 12000),
  main = "Sales data for Branches for the same company
per month",
  xlab = "Month",
  ylab = "Sales",
  type = "b",
  pch = 20,
  xaxt = "n",
  frame.plot = F,
  lwd = 2
)

axis(1, at = seq(1, length(Month)), labels = Month)

lines(sales[, 3], col = "red", type = "b", pch = 20, lwd = 2)

lines(sales[, 4], col = "blue", type = "b", pch = 20, lwd = 2)

lines(sales[, 5], col = "orange", type = "b", pch = 20, lwd = 2)

legend("bottom",
  legend = c("A", "B", "C", "D"), lwd = 2, pch = 20, col = c(
    "black", "red", "blue",
    "orange"
  ), ncol = 4, bty = "n", cex = 0.8, text.col = c(
    "black", "red", "blue",
    "orange"
  ), inset = 0.01
)
detach(sales)
```

# Pie Chart

```{r}
attach(iris)
table1 <- table(Species)
labs <- paste(names(table1), "\n", table1)
pie(table1, labels = labs, main = "Pie Chart of Species")
detach(iris)
```

# Stem and Leaf
```{r}
stem(faithful[, "eruptions"], scale = 1.5)
```

```{r}
sum(between(faithful[, "eruptions"], 2.3, 2.399
          ))
```